Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
added reference

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute values are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.

>>>>

A discrete-time system as \eqref{eq:closedloopss} is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues of the closed-loop matrix $A_d - B_d K$) are inside the unity circle in the complex plane, 
{\it i.e.} iff their absolute value are less than one~\cite{astrom1997computer}. 
In this paper, we express the stability specification $\phi_{stability}$ in terms of a check known as Jury's criterion \cite{fadali}. 
This condition boils down to an easy algebraic formula to select the entries of matrix $K$, 
so that the closed-loop dynamics are shaped as desired. 
A detailed description of this specification can be found in the Appendix~\ref{sec:appendix-stability}.
